---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jgNutritionTools

<!-- badges: start -->
<!-- badges: end -->

The goal of jgNutritionTools is to provide a toolset for the analysis and management of human health and physical data.

## Installation

You can install the development version of jgNutritionTools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MacDonaldMichael1/jgNutritionTools")
```

## Examples

Assuming a valid DB connection has been made:

1. Use helper function to display country year combinations

```{r conn, include=FALSE}
require(RMySQL)

lapply(dbListConnections(MySQL()),
       dbDisconnect)
dbListConnections(MySQL())


mydb <- dbConnect(drv = MySQL(),
                  host = "jgnutritionsec.ctincuwvvm7w.us-west-2.rds.amazonaws.com",
                  default.file = path.expand("~/.my.cnf"),
                  group = "admin")
```

```{r example, message = F}
library(jgNutritionTools)
library(tidyverse)
## Show country and DHSYEAR combos for DHS surveys with country code
getCountryYearCom(mydb) %>% head()

```   
2. Retrieve CHIRPS precipitation data for Burkina Faso in 2003
```{r echo=TRUE, eval = F}
getPrecip(conn = mydb, countryCode = "854",
          Year = "2003",
          timeFrame = 0)
```
## Acknowledgements 

A portion of the source code for functions in the `jgNutritionTools` package was developed using code from the [ropensci/chirps](https://github.com/ropensci/chirps) package. We thank these developers for providing this code under the MIT licence.
